---
output: md_document
---

Rep_Peer_Assignment Week 2 
============================

## Question 1

### Histogram Plot for number of steps per day

```{r}
library(dplyr)
activity <- read.csv("activity.csv")
steps_by_date <- activity %>%        ##Formatting the data to plot Histogram
                 group_by(date) %>%
                 summarise(steps =  sum(steps)) %>%
                 na.omit()

 steps_by_date_hist <- hist(steps_by_date$steps, xlab = "steps",
                            breaks = 20)
 
 steps_by_date_hist
    
```

### Mean and Median for the number of steps grouped by date 

```{r}

raw_data_mean <- mean(steps_by_date$steps)

raw_data_mean

raw_data_median <- median(steps_by_date$steps)

raw_data_median
```



## Question 2

### Grouping the data by the interval and producing a line plot

```{r}
library(ggplot2)
steps_interval <- activity %>%
                  select(interval, steps) %>%
                  na.omit() %>%
                  group_by(interval) %>%
                  summarise(steps = mean(steps))

g <- ggplot(steps_interval, aes(interval, steps)) + geom_line()

g
```

### Which 5 minute interval contains maximum number of steps

```{r}

max_steps_interval <- steps_interval[which(steps_interval$steps == max(steps_interval$steps)),]

max_steps_interval
```


## Question 3

### Calculating number of rows with missing values in original dataset

```{r}
sum(is.na(activity))
```

### Imputing the rows using the impute function from Hmisc Package

```{r}
library(Hmisc)
activity_imputed <- activity
activity_imputed$steps <- impute(activity_imputed$steps, fun = mean)
sum(is.na(activity_imputed))
```

### Ploting a Histogram from imputed data 

```{r}
steps_by_date_imputed <- activity_imputed %>% 
                 group_by(date) %>%
                 summarise(steps =  sum(steps)) %>%
                 na.omit()

 steps_by_date_hist_imputed <- hist(steps_by_date_imputed$steps, xlab = "steps", breaks = 20)
 
 steps_by_date_hist_imputed

```

### Comparing Mean and Median of imputed data with raw data

```{r}
print("Raw Data Mean :")
raw_data_mean
print("Imputed Data Mean :")
mean(steps_by_date_imputed$steps)
print("Raw Data Median :")
raw_data_median
print("Imputed Data median :")
median(steps_by_date_imputed$steps)
```


## Question 4

### Separating the data into weekend and week days

```{r}
activity_imputed$date <- as.Date(as.character(activity_imputed$date))
activity_imputed$weekday <- weekdays(activity_imputed$date)
activity_imputed$weekend <- ifelse(activity_imputed$weekday=="Saturday" | activity_imputed$weekday=="Sunday", "Weekend", "Weekday" )
head(activity_imputed)
```

### Subsetting the data set by weekend and steps

```{r}

activity_imputed_subset <- aggregate(activity_imputed$steps , by= list(activity_imputed$weekend, activity_imputed$interval), na.omit(mean))

names(activity_imputed_subset) <- c("weekend", "interval", "steps")

head(activity_imputed_subset)
```

### Plotting a panel plot to differentiate between Weekend and Weekdays

```{r}
g2 <- ggplot(activity_imputed_subset, aes(interval, steps, color = weekend)) + geom_line() + facet_grid(weekend~.) + xlab("Interval") + ylab("Steps")

g2

```

